\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-16 paper/ms.tex
Julia model section

\code{-c <value>}\\
Standard DNS creates levels with a volume ratio of approximately
$e\approx 2.71828$. To use a different value, such as 10, use this option.
In our experience, \code{-c 10} tends to work better than the default
value on problems with a large information.
The output units remain in nats.
This option is incompatible with setting the maximum number of levels to 0
(automatic) in the OPTIONS file.
\\

@@

\section{Specifying models in Julia}

>>>>

\code{-c <value>}\\
Standard DNS creates levels with a volume ratio of approximately
$e\approx 2.71828$. To use a different value, such as 10, use this option.
In our experience, \code{-c 10} tends to work better than the default
value on problems with a large information $\mathcal{H}$.
The output units remain in nats.
This option is incompatible with setting the maximum number of levels to 0
(automatic) in the OPTIONS file.
\\

@@

\section{Specifying models in Julia}
Experimental support for model specification in the
\proglang{Julia} language is provided, with an example given in the
code/Templates/JuliaModel directory.
Set an enviroment variable {\tt JULIA\_PATH} to the directory on your
system that contains the libraries {\tt libjulia.so} and
{\tt sys.so}. Set another environment variable {\tt JULIA\_INCLUDE\_PATH}
to the directory where the \proglang{Julia} header files are located
(do not include the final {\tt julia} directory in this path).

The log likelihood is specified in {\tt julia\_model.jl}, as a function
called {\tt log\_likelihood} that takes a {\tt Vector::Float64} as an argument
and returns a {\tt Float64}. You should assume that the priors for the
parameters are independent Uniform(0, 1) distributions (sensible default
proposals are used). To use a different prior, transform the parameters inside
your {\tt log\_likelihood} function before using them.
You may add other functions to {\tt julia\_model.jl}, for example to load
a dataset to refer to in your {\tt log\_likelihood}. The example in
the repository is the ``SpikeSlab'' likelihood from \citet{dnest}.

You can compile the model by invoking {\tt make}
from the {\tt JuliaModel} directory.
Only a single thread is supported when running \proglang{Julia}
models.
